On the link between functional traits and growth rate: meta-analysis shows effects change with plant size, as predicted

### 2016-02-21 MS.tex

We thank Andrea Stephens for helpful comments on the meta-analyses, and Sean Gleason et al for pre-publication access to their data. Charles Warren and Jordi Mart{\'{i}}nez-Vilalta kindly provided additional information about their published results. This work was funded by the Australian Research Council through a fellowship to M.W, a discovery grant to D.S.F and a Macquarie University Research Excellence Scholarship and L’Oreal UNESCO FWIS Fellowship to E.F.G.

@@

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig2.pdf}
\caption{ The range of plant sizes and stages recorded in original publications (horizontal coloured lines), compared to standardised thresholds used in the analysis (vertical black lines). Horizontal line segments indicate the size range (max., min.) of the plants used to measure growth. Horizontal line colours refer to the original stage attributed by the authors .The solid vertical lines indicate the thresholds used to classify plants in one of three stages in our meta-analyses. Studies marked with a “*” were those where stage was changed or assigned, compared to the original publication.}
\label{fig:fig2}
\end{figure}

>>>>

We thank Andrea Stephens for helpful comments on the meta-analyses, and Sean Gleason et al for pre-publication access to their data. Charles Warren and Jordi Mart{\'{i}}nez-Vilalta kindly provided additional information about their published results. This work was funded by the Australian Research Council through a fellowship to M.W, a discovery grant to D.S.F and a Macquarie University Research Excellence Scholarship and L'Oreal UNESCO FWIS Fellowship to E.F.G.

@@

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig2.pdf}
\caption{ The range of plant sizes and stages recorded in original publications (horizontal coloured lines), compared to standardised thresholds used in the analysis (vertical black lines). Horizontal line segments indicate the size range (max., min.) of the plants used to measure growth. Horizontal line colours refer to the original stage attributed by the authors .The solid vertical lines indicate the thresholds used to classify plants in one of three stages in our meta-analyses. Studies marked with a ``*'' were those where stage was changed or assigned, compared to the original publication.}
\label{fig:fig2}
\end{figure}

### 2016-02-21 ms-suppinfo.Rnw

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA6c.pdf}
\caption{Effects size on the correlation between growth and traits of plant stage (mod1), growth measurement (mod2), vegetation type (mod3), and experiment type (mod4). a) Specific leaf area (SLA), b) Wood density (WD),c) Assimilation rate of CO2 (Aarea), d) Seed mass, and e) Asymptotic maximum height (Hmax). The effect size (z + 95\%CI) is reported for each class, and models are fitted by restricted max likelihood (REML). Abbreviation: GR = growth rate and RGR = relative growth rate, measured in diameter (D), height (H), mass(M), cross section area (CSA) and volume (V), across GF: coefficient of correlation measured on tree in mixture with other growth form. AIC: Akaike information criterion corresponds to the quality of each model, and allow a comparison between models. Smallest is the AIC better is the model. Results shown here are from ``ideal'' subset of data (for details see ``Material and Methods''). ``n'' indicates number of correlation r reported.}
\label{fig:figA6}
\end{figure}

@@

For the case of seedlings, the growth equations can be simplified considerably. Turnover of all tissues and allocation to reproduction have not yet begun. It is also common to assume all respiration rates are proportional to leaf area. Biomass growth rate in seedling then becomes a linear function of leaf area:
\begin{equation}\label{eq:eq1_seedlings}
{\frac{\ud M_{\rm t}}{\ud t}}  \approx  A_{\rm l} \, y \, (p - r_{\rm l}).
\end{equation}

The \textbf{relative growth rate in mass} $({\rm RGR}_{{\rm mass}})$ in seedlings can be obtained by dividing both sides of this simplified eq \ref{eq:eq1_seedlings} by the total mass of living tissues $M_{\rm t}$. The outcome is equivalent to the classical partitioning of RGR \citep{Lambers:1992bj, Cornelissen:1998ta}:
\begin{equation}\label{eq:eq1_seedlings_RGR}
{\rm RGR}_{{\rm mass}}  \approx {\rm NAR} \times  {\rm SLA} \times  {\rm LMF},
\end{equation}
where net assimilation rate NAR = $y \, (p - r)$, SLA = $A_{\rm l}/ M_{\rm l}$ and leaf mass fraction LMF = $M_{\rm l}/ M_{\rm t}$.

>>>>

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA6c.pdf}
\caption{Effects size on the correlation between growth and traits of plant stage (mod1), growth measurement (mod2), vegetation type (mod3), and experiment type (mod4). a) Specific leaf area (SLA), b) Wood density (WD),c) Assimilation rate of CO2 (Aarea), d) Seed mass, and e) Asymptotic maximum height (Hmax). The effect size (z + 95\%CI) is reported for each class, and models are fitted by restricted max likelihood (REML). Abbreviation: GR = growth rate and RGR = relative growth rate, measured in diameter (D), height (H), mass(M), cross section area (CSA) and volume (V), across GF: coefficient of correlation measured on tree in mixture with other growth form. AIC: Akaike information criterion corresponds to the quality of each model, and allow a comparison between models. The smaller the AIC, the better the model is. Results shown here are from ``ideal'' subset of data (for details see ``Material and Methods''). ``n'' indicates number of correlation r reported.}
\label{fig:figA6}
\end{figure}

@@

For the case of seedlings, the growth equations can be simplified considerably. Turnover of all tissues and allocation to reproduction have not yet begun. It is also common to assume all respiration rates are proportional to leaf area. Biomass growth rate in seedling then becomes a linear function of leaf area:
\begin{equation}\label{eq:eq1_seedlings}
{\frac{\ud M_{\rm a} }{\ud t}}  \approx  A_{\rm l} \, y \, (p - r_{\rm l}).
\end{equation}

The \textbf{relative growth rate in mass} $({\rm RGR}_{{\rm mass}})$ in seedlings can be obtained by dividing both sides of this simplified eq \ref{eq:eq1_seedlings} by the total mass of living tissues $M_{\rm a} $. The outcome is equivalent to the classical partitioning of RGR \citep{Lambers:1992bj, Cornelissen:1998ta}:
\begin{equation}\label{eq:eq1_seedlings_RGR}
{\rm RGR}_{{\rm mass}}  \approx {\rm NAR} \times  {\rm SLA} \times  {\rm LMF},
\end{equation}
where net assimilation rate NAR = $y \, (p - r)$, SLA = $A_{\rm l}/ M_{\rm l}$ and leaf mass fraction LMF = $M_{\rm l}/ M_{\rm a} $.
